---
title: "About"
output:
  workflowr::wflow_html:
    toc: TRUE
editor_options:
  chunk_output_type: console
---

# introduction

this is a base project to simply show creating the supplementary data files and show casing how this simple concept can be used to create maintainable that is easily extendable and has the tools required to manage complexity.

to understand this document browse it as if you would any website; exploring is important and baked into it

## my musings on managing complexity

> anyone can write code a computer can understand; the real challenge is writing in a way that humans can

> when a field becomes sufficiently advanced it reinvents algebra; so lets skip straight to algebra

we write software/code to manage complexities; without these tools it would be impossible to do much of all we do; but at the end of the day it is just a tool and picking the right tool for the job is important. when the only tool you have is a hammer everything looks like a nail below I will outline some tools that will help us manage the complexities of working in PGDP; especially remotely.

### Tool \#1 Rmarkdown

this document you are reading is a rmarkdown; it is magic as far as I am concerned it combines some powerful yet simple ideas but it ultimately allows you to communicate your purpose; documentation , logic , and code, work report, management tool, training document, research paper, data product, visualization tool, presentation material, panflet and hand out generator, report tool and many other uses in one manageable place; seriously just watch [this](https://www.youtube.com/watch?v=qLEkUjxk7e8). it is truly a marvel. more on literate programming [here](https://en.wikipedia.org/wiki/Literate_programming){#literateprogramming .documentation style="color:red"} for more info but the jist is this

> **Literate programming** is a [programming paradigm](https://en.wikipedia.org/wiki/Programming_paradigm "Programming paradigm") introduced by [Donald Knuth](https://en.wikipedia.org/wiki/Donald_Knuth "Donald Knuth") in which a [computer program](https://en.wikipedia.org/wiki/Computer_program "Computer program") is given an explanation of its logic in a [natural language](https://en.wikipedia.org/wiki/Natural_language "Natural language"), such as English, interspersed with [snippets](https://en.wikipedia.org/wiki/Snippet_(programming) "Snippet (programming)") of [macros](https://en.wikipedia.org/wiki/Macro_(computer_science) "Macro (computer science)") and traditional [source code](https://en.wikipedia.org/wiki/Source_code "Source code"), from which [compilable](https://en.wikipedia.org/wiki/Compiler "Compiler") source code can be generated.^[[1]](https://en.wikipedia.org/wiki/Literate_programming#cite_note-TCJ_LP-1)^ The approach is used in [scientific computing](https://en.wikipedia.org/wiki/Scientific_computing "Scientific computing") and in [data science](https://en.wikipedia.org/wiki/Data_science "Data science") routinely for [reproducible research](https://en.wikipedia.org/wiki/Reproducible_research "Reproducible research") and [open access](https://en.wikipedia.org/wiki/Open_access "Open access") purposes.^[[2]](https://en.wikipedia.org/wiki/Literate_programming#cite_note-2)^ Literate programming tools are used by millions of programmers today

rmarkdown gives you headings that collapse to further structure this, allowing you to jump between section very quickly

#### showing off what it can do in a static website

this here is a piece of code using a package called ggplot2; the data is from the world bank and is called `gapminder` it is a simple data set on life expectancy and gdp per country.

ggplot uses a grammar for describing visual components

```{r showing rmarkdowns utility, echo=TRUE}
library(ggplot2)
data(gapminder, package = "gapminder")
gg <- ggplot(gapminder, aes(gdpPercap, lifeExp, color = continent)) +
  geom_point(aes(size = pop, frame = year, ids = country)) +
  scale_x_log10()
plotly::ggplotly(gg)
```

#### adjusting the example above for our section

```{r showing rmarkdowns utility PGDP style, echo=TRUE}
library(ggplot2)
library(tidyverse)

pgdp <- cansim::get_cansim( "36-10-0402-02") %>% select(REF_DATE,GEO,Value,VALUE,`North American Industry Classification System (NAICS)`) %>% pivot_wider(names_from = Value, values_from = VALUE) 
#
gg <- ggplot(pgdp, aes(`Contributions to percent change`, `Current dollars`, color = GEO)) +
  geom_point(aes(size = `Chained (2012) dollars`, frame = REF_DATE, ids = `North American Industry Classification System (NAICS)`)) +
  scale_x_log10()
plotly::ggplotly(gg)
```

use string matching to only 2 digit naics and manufacturing and bring in MSM data

#### useful links on Rmarkdown and R

[good beginner book for learning R with lots of examples](https://r4ds.had.co.nz/)

[R Markdown Cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/)

[R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/)

## Tool \#2 git

git allows us to effectively track what we have worked on and go back if we need to; it also helps us keep track of versions and also enables to work collaboratively in a tractable and manageable way. scroll to the and click on the black box workflowr past versions; there you can see track all that I have done to this page.

### useful links on git

[interesting interactive way to try it out should take 45 min to finish](https://learngitbranching.js.org/ "a simple website to teach you git"){#documentation}

[fun little book by UBC on using it with R](https://happygitwithr.com/)

# technical notes

## tools used

this project uses `workflowr`, `git`and `rmarkdown` to ensure reproducibility; documentation and version history. alternatively it can be hosted on github or `gitlab`(on net a)

## 

Describe your project. hell oworld
