---
title: "Provincial_view"
author: "Arman Attaran"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
params: 
 Developer_mode: FALSE
 tests: TRUE
---

# Introduction

in this document I will create a view based on the following tables

-   contribution to total economy

-   population [17-10-0009-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1710000901 "Table 17-10-0009-01").

-   immigration [17-10-0008-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1710000801 "Table 17-10-0008-01").

-   labor force Statistics Canada, table [14-10-0327-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1410032701 "Table 14-10-0327-01").

-   Farms, by operation type [32-10-0403-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3210040301 "Table 32-10-0403-01").

-   Aquaculture in Canada [32-10-0107-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3210010701 "Table 32-10-0107-01").

-   Manufacturing industries [16-10-0117-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1610011701 "Table 16-10-0117-01").

-   International merchandise trade by province, commodity, and Principal Trading Partners 12-10-0119-01

-   Investment in Building Construction(monthly) [34-10-0175-01](https://www150.statcan.gc.ca/t1/tbl1/en/cv.action?pid=3410017501)

-   Industrial capacity utilization rates, by industry [16-10-0109-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1610010901)

-   Building permits, by type of structure and type of work [34-10-0066-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3410006601&pickMembers%5B0%5D=1.7&pickMembers%5B1%5D=3.1&pickMembers%5B2%5D=4.1&pickMembers%5B3%5D=5.1&cubeTimeFrame.startMonth=01&cubeTimeFrame.startYear=2019&cubeTimeFrame.endMonth=12&cubeTimeFrame.endYear=2020&referencePeriods=20190101%2C20201201)

-   Employment and average weekly earnings (including overtime) for all employees by province and territory, monthly, seasonally adjusted [14-10-0223-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1410022301&pickMembers%5B0%5D=2.2&pickMembers%5B1%5D=3.2&cubeTimeFrame.startMonth=01&cubeTimeFrame.startYear=2019&cubeTimeFrame.endMonth=11&cubeTimeFrame.endYear=2020&referencePeriods=20190101%2C20201101)

## set up

in this section I will set up the foundation for the program; it is broke up into 3 parts; package dependency and path; functions,and finally code lists.

### Package dependency

in this section I will manage dependencies ( the packages used in this project; in R you need to state what you will use (kinda) and here we will simply state them) these will have to be installed for the program to run properly. if you run this in the cloud the commands below should be sufficient. if you uncomment the first 5 lines

```{r setup, message=FALSE, warning=FALSE, include=params$Developer_mode}


# install.packages("tidyverse")
# install.packages("DT")
# install.packages("cansim")
# install.packages("janitor")
# install.packages("here")

library(tidyverse) # all the tools I need to manipulate and graph data.
library(DT) # for creating the interactive table
library(janitor) # for cleaning table names
library(cansim) # for downloading NDM tables
library(here) # for managing folder paths.
# paramters for the project 
from_this_year <- "2016-12-29"

## codelists 

two_digit_naics_code <- c("[11]", "[21]", "[22]", "[23]", "[31-33]", "[41]", "[44-45]", "[48-49]", "[51]", "[52]", "[53]", "[54]", "[55]", "[56]", "[61]", "[62]", "[71]", "[72]", "[81]", "[91]")

provinces <- c(
  "Alberta", "British Columbia", "Canada", "Manitoba", "New Brunswick", "Newfoundland and Labrador", "Nova Scotia", "Ontario", "Prince Edward Island", "Quebec", "Saskatchewan", "Northwest Territories", "Nunavut", "Yukon", "Yellowknife, Northwest Territories", "Whitehorse, Yukon", "Iqaluit, Nunavut")
#table numbers 
pgdp_table_number <- "36-10-0402"
annual_lfs_table_number <- "14-10-0023-01" 
employment_by_industury_table_number_annual <- "14-10-0202-01"
population_table_number <- "17-10-0005-01"
farms_table_number <- "32-10-0403-01"
grain_shipment_table_number <- "32-10-0351-01"
building_construction_table_number <- "34-10-0175-01"
building_permits_table_number <- "34-10-0066-01 "
trade_table_number <- "12-10-0119-01"
immigration_table_number <- "17-10-0008-01"
aquaculture_table_number <- "32-10-0107-01"
Manufacturing_indusries_table_number <- "16-10-0117-01"
cpi_table_number <- "18100005"
 

#function 
interactive_table <- function(data) {
  DT::datatable(
    {{ data }},
    extensions = c("ColReorder", "Buttons"), options = list(
      colReorder = TRUE,
      dom = "Bfrtip",
      buttons = c("copy", "csv", I("colvis")),
      searchHighlight = TRUE,
      search = list(regex = TRUE)
    ),
    filter = "top"
  )
}

```

### paths

all the files in this program will now be created relative to where you run this script; it will create all the necessary subflorder and files from the location below

```{r}
here()
```

### codelists

stating what the code lists are for the project to sort and query data from; if you want to add some thing for the table to include you can simple add it here and it should work;. it is designed this way to make this program more extendable, and maintainable. the added complexity is worth it

```{r, include=params$Developer_mode, paged.print=FALSE}

provincial_two_digit_cord <- c("1.1.1", "1.1.2", "1.1.3", "1.1.4", "1.1.5", "1.1.6", "1.1.7", "1.1.8", "1.1.9", "1.1.10", "1.1.11", "1.1.12", "1.1.13", "1.1.14", "1.1.15", "1.1.16", "1.1.17", "1.1.18", "1.1.19", "1.1.20", "1.1.21", "2.1.1", "2.1.2", "2.1.3", "2.1.4", "2.1.5", "2.1.6", "2.1.7", "2.1.8", "2.1.9", "2.1.10", "2.1.11", "2.1.12", "2.1.13", "2.1.14", "2.1.15", "2.1.16", "2.1.17", "2.1.18", "2.1.19", "2.1.20", " 2.1.21", "3.1.1", "3.1.2", "3.1.3", "3.1.4", "3.1.5", "3.1.6", "3.1.7", "3.1.8", "3.1.9", "3.1.10", "3.1.11", "3.1.12", "3.1.13", "3.1.14", "3.1.15", "3.1.16", "3.1.17", "3.1.18", "3.1.19", "3.1.20", "3.1.21", "4.1.1", "4.1.2", "4.1.3", "4.1.4", "4.1.5", "4.1.6", "4.1.7", "4.1.8", "4.1.9", "4.1.10", "4.1.11", "4.1.12", "4.1.13", "4.1.14", "4.1.15", "4.1.16", "4.1.17", "4.1.18", "4.1.19", "4.1.20", "4.1.21", "5.1.1", "5.1.2", "5.1.3", "5.1.4", "5.1.5", "5.1.6", "5.1.7", "5.1.8", "5.1.9", "5.1.10", "5.1.11", "5.1.12", "5.1.13", "5.1.14", "5.1.15", "5.1.16", "5.1.17", "5.1.18", "5.1.19", "5.1.20", "5.1.21", "6.1.1", "6.1.2", "6.1.3", "6.1.4", "6.1.5", "6.1.6", "6.1.7", "6.1.8", "6.1.9", "6.1.10", "6.1.11", "6.1.12", "6.1.13", "6.1.14", "6.1.15", "6.1.16", "6.1.17", "6.1.18", "6.1.19", "6.1.20", "6.1.21", "7.1.1", "7.1.2", "7.1.3", "7.1.4", "7.1.5", "7.1.6", "7.1.7", "7.1.8", "7.1.9", "7.1.10", "7.1.11", "7.1.12", "7.1.13", "7.1.14", "7.1.15", "7.1.16", "7.1.17", "7.1.18", "7.1.19", "7.1.20", "7.1.21", "8.1.1", "8.1.2", "8.1.3", "8.1.4", "8.1.5", "8.1.6", "8.1.7", "8.1.8", "8.1.9", "8.1.10", "8.1.11", "8.1.12", "8.1.13", "8.1.14", "8.1.15", "8.1.16", "8.1.17", "8.1.18", "8.1.19", "8.1.20", "8.1.21", "9.1.1", "9.1.2", "9.1.3", "9.1.4", "9.1.5", "9.1.6", "9.1.7", "9.1.8", "9.1.9", "9.1.10", "9.1.11", "9.1.12", "9.1.13", "9.1.14", "9.1.15", "9.1.16", "9.1.17", "9.1.18", "9.1.19", "9.1.20", "9.1.21", "10.1.1", "10.1.2", "10.1.3", "10.1.4", "10.1.5", "10.1.6", "10.1.7", "10.1.8", "10.1.9", "10.1.10", "10.1.11", "10.1.12", "10.1.13", "10.1.14", "10.1.15", "10.1.16", "10.1.17", "10.1.18", "10.1.19", "10.1.20", "10.1.21", "11.1.1", "11.1.2", "11.1.3", "11.1.4", "11.1.5", "11.1.6", "11.1.7", "11.1.8", "11.1.9", "11.1.10", "11.1.11", "11.1.12", "11.1.13", "11.1.14", "11.1.15", "11.1.16", "11.1.17", "11.1.18", "11.1.19", "11.1.20", "11.1.21", "12.1.1", "12.1.2", "12.1.3", "12.1.4", "12.1.5", "12.1.6", "12.1.7", "12.1.8", "12.1.9", "12.1.10", "12.1.11", "12.1.12", "12.1.13", "12.1.14", "12.1.15", "12.1.16", "12.1.17", "12.1.18", "12.1.19", "12.1.20", "12.1.21", "13.1.1", "13.1.2", "13.1.3", "13.1.4", "13.1.5", "13.1.6", "13.1.7", "13.1.8", "13.1.9", "13.1.10", "13.1.11", "13.1.12", "13.1.13", "13.1.14", "13.1.15", "13.1.16", "13.1.17", "13.1.18", "13.1.19", "13.1.20", "13.1.21", "14.1.1", "14.1.2", "14.1.3", "14.1.4", "14.1.5", "14.1.6", "14.1.7", "14.1.8", "14.1.9", "14.1.10", "14.1.11", "14.1.12", "14.1.13", "14.1.14", "14.1.15", "14.1.16", "14.1.17", "14.1.18", "14.1.19", "14.1.20", "14.1.21")


```

### table numbers

if you have any tables to add please add it here; it will make it easier to maintain this program

```{r table numbers}

  
```

### functions

here I will describe the functions required in the project. the most important one is the one for creating interactive tables in the browser that allow you to change which columns to show and to search through tables.

it is important for the search function and performance for the columns to be categories and/or numerics.

TODO: find a way to handle sig dig

```{r setup functions , include=FALSE}
interactive_table <- function(data) {
  DT::datatable(
    {{ data }},
    extensions = c("ColReorder", "Buttons"), options = list(
      colReorder = TRUE,
      dom = "Bfrtip",
      buttons = c("copy", "csv", I("colvis")),
      searchHighlight = TRUE,
      search = list(regex = TRUE)
    ),
    filter = "top"
  )
}
# test
interactive_table(gapminder::gapminder)

# summarytools::view(dfSummary(LFS))  for exploring tables
```

# Macro economic accounts

i will attempt to import and clean all the tables \#\#\# PGDP here I will be working with Provincial GDP

## GDP measures IAD

here I will include the tables by IAD

### Provincial GDP CPC

```{r PGDP}
pgdp_table_number <- "36-10-0402"
pgdp <- cansim::get_cansim_ndm(pgdp_table_number)
pgdp <- janitor::clean_names(pgdp)
pgdp %>%
  select(ref_date, geo, north_american_industry_classification_system_naics, value, hierarchy_for_north_american_industry_classification_system_naics, coordinate, classification_code_for_north_american_industry_classification_system_naics, value_2) %>%
  mutate(ref_date = lubridate::make_date(ref_date)) %>%
  rename(CPC = value_2) %>%
  filter(ref_date > from_this_year) %>%
  filter(value == "Contributions to percent change") %>%
  select(!value) %>%
  filter(classification_code_for_north_american_industry_classification_system_naics %in% c(two_digit_naics_code)) %>%
  group_by(ref_date, north_american_industry_classification_system_naics, geo) -> clean_PGDP
# maybe wait till the end to convert the tables to save some space

interactive_table(clean_PGDP)
# data.table::fwrite(here("output", str_glue("Table_{tablenumber}_CPI_by_province_product_groups_{params$from_this_year}-{params$to_this_year}")))
```

#### Provincial GDP

```{r}
pgdp_table_number <- "36-10-0402"
pgdp <- cansim::get_cansim_ndm(pgdp_table_number)
pgdp <- janitor::clean_names(pgdp)
pgdp %>%
  select(ref_date, geo, north_american_industry_classification_system_naics, value, value_2) %>% 
  mutate(ref_date = lubridate::make_date(ref_date)) %>% 
  pivot_wider(names_from = value, values_from = value_2) %>%  filter(ref_date > from_this_year) -> clean_PGDP
clean_PGDP %>% data.table::fwrite(here::here("output", str_glue("Provincial_GDP_36-10-0402.csv")))
# maybe wait till the end to convert the tables to save some space

```

#### provincial GDP for master table

```{r Provincial GDP mastertable}
pgdp
pgdp %>%
  select(ref_date, geo, north_american_industry_classification_system_naics, value, value_2) %>%
  mutate(ref_date = lubridate::make_date(ref_date)) %>%
  rename(CPC = value_2) %>%
  filter(ref_date > from_this_year) %>%
  filter(value == "Contributions to percent change") %>%
  select(!value) %>%
  filter(north_american_industry_classification_system_naics == "All industries [T001]") %>%
  pivot_wider(names_from = north_american_industry_classification_system_naics, values_from = CPC) %>%
  janitor::clean_names() %>%
  rename(CPC_All_industries = all_industries_t001) -> master_pgdp
```

### MGDP real GDP by industry

add MGDP

```{r}

```

### population

```{r population}

library(summarytools)
population <- cansim::get_cansim_ndm(population_table_number)
population %>%
  janitor::clean_names() %>%
  select(1, 2, 4, 5, 12) %>%
  rename(population = value) %>%
  mutate(ref_date = lubridate::make_date(ref_date)) %>%
  filter(ref_date > from_this_year) %>%
  filter(age_group == "All ages") %>%
  filter(sex == "Both sexes") %>%
  select(1, 2, 5) -> clean_population
# view(dfSummary(clean_population))
interactive_table(clean_population)
clean_population %>%
data.table::fwrite(here::here("output", str_glue("Population_{population_table_number}.csv")))
```

### **Capital and repair expenditures, non-residential tangible assets, by industry and geography** 

34-10-0035-01

im not sure where this fits in

### Trade monthly

This is the YOY percentage change difference for the monthly trade by NAPC I will create the annual series tomorrow. simply sum it over the year. it seems to be what the chief economist did and also it makes sense since it is already seasonally adjusted

```{r Trade Monthly}
trade <- cansim::get_cansim_ndm(trade_table_number)
trade <- janitor::clean_names(trade)
trade %>%
  select(ref_date, geo, trade, north_american_product_classification_system_napcs, principal_trading_partners, value) %>%
  mutate(ref_date = parse_date(ref_date, "%Y-%m")) %>%
  filter(ref_date > from_this_year) %>%
  pivot_wider(names_from = trade, values_from = value) %>%
  janitor::clean_names() %>%
  arrange(north_american_product_classification_system_napcs, principal_trading_partners, geo, ref_date) %>%
  group_by(north_american_product_classification_system_napcs, principal_trading_partners, geo) %>%
  mutate(yoy_pct_change_import = ((import / lag(import, n = 12, order_by = ref_date)) * 100) - 100) %>%
  mutate(yoy_first_dif_import = (import - lag(import, n = 12, order_by = ref_date))) %>%
  mutate(yoy_pct_change_export = ((domestic_export / lag(domestic_export, n = 12, order_by = ref_date)) * 100) - 100) %>%
  mutate(yoy_first_dif_export = (domestic_export - lag(domestic_export, n = 12, order_by = ref_date))) %>% data.table::fwrite(here::here("output", str_glue("Trade_Monthly{trade_table_number}.csv")))

  
  # group_by(3,4,2) %>%
  
#data.table::fwrite(here::here("delete", str_glue("Table_{trade_table_number}_Trade_full_table_from{from_this_year}.csv")))
```

### Trade annual

annualized trade; run this in mid feb to make sure all the months are there for a reference year. doing so earlier will result in the most recent year being underepesented the best choice is to use moving average or an estimated value below is the raw trade data from NDM; it comes monthly and with a lot of data I filter out most of it for this provincial view

```{r Trade Raw}
# make sure you run this after the december release; 8 weeks after reference period is the release
library(tidyverse)
library(tsibble)
library(lubridate)
trade <- cansim::get_cansim_ndm(trade_table_number)
trade <- janitor::clean_names(trade)
trade %>%
  select(ref_date, geo, trade, north_american_product_classification_system_napcs, principal_trading_partners, value) %>%
  mutate(ref_date = parse_date(ref_date, "%Y-%m")) %>%
  filter(ref_date > from_this_year) %>%
  pivot_wider(names_from = trade, values_from = value) %>%
  janitor::clean_names() -> clean_trade
data_tsbl <- as_tsibble(clean_trade, key = c(north_american_product_classification_system_napcs, principal_trading_partners, geo))
data_tsbl %>%
  group_by_key() %>%
  index_by(year_month = ~ year(.)) %>%
  summarise(
    import = sum(import, na.rm = TRUE),
    export = sum(domestic_export, na.rm = TRUE)
  ) -> annual_trade
# saving the CSV {} between these things the program will put in R code
annual_trade %>% data.table::fwrite(here::here("output", str_glue("annual_trade_table_{trade_table_number}.csv")))
```

#### annual trade filtered and left joined into master table

```{r joining trade to the master}
as_tibble(annual_trade) %>%
  filter(principal_trading_partners == "All countries") %>%
  filter(north_american_product_classification_system_napcs == "Total of all merchandise") %>%
  rename(ref_date = year_month) %>%
  mutate(ref_date = lubridate::make_date(ref_date)) %>%
  select(geo, ref_date, import, export) -> master_trade
left_join(clean_population, master_trade) %>% left_join(master_pgdp) -> master_provincial_table


```

### Immigration table

```{r Immigration }
Immigration <- cansim::get_cansim_ndm(immigration_table_number)
Immigration <- janitor::clean_names(Immigration)
Immigration %>%
  select(ref_date, geo, components_of_population_growth, value) %>%
  mutate(ref_date = parse_date(ref_date, "%Y /%Y")) %>%
  filter(ref_date > from_this_year) %>%
  pivot_wider(names_from = components_of_population_growth, values_from = value) %>%
  group_by(geo) %>%
  clean_names() -> clean_immigration
master_provincial_table %>%
  left_join(clean_immigration) -> master_provincial_table
```

### construction

all construction numbers are for total type of work and are in unadjusted K dollar mabye I should just use 23A_K\_ind

```{r construction}

construction <- cansim::get_cansim_ndm(building_construction_table_number)
construction <- janitor::clean_names(construction)
construction %>%
  select(ref_date, geo, type_of_structure, type_of_work, investment_value, value) %>%
  mutate(ref_date = parse_date(ref_date, "%Y-%m")) %>%
  filter(ref_date > from_this_year) %>%
  filter(geo %in% provinces) %>%
  filter(type_of_work == "Types of work, total") %>% 
  select(!type_of_work) %>%
  filter(investment_value %in% c("Unadjusted - constant")) %>%
  select(!investment_value) %>%
  filter(type_of_structure %in% c("Total residential and non-residential", "Total residential", "Total non-residential")) %>%
  pivot_wider(names_from = type_of_structure, values_from = value) %>%
  clean_names() %>%
  rename_if(is.numeric, funs(str_c(., "_investment_unadjusted_K$"))) -> clean_construction

data_tsbl <- as_tsibble(clean_construction, key = c(geo))

data_tsbl %>%
  group_by_key() %>%
  index_by(year_month = ~ year(.)) %>%
  summarise(across(where(is.numeric),list( a = sum))) -> master_construction
master_construction %>%
  as_tibble() %>% rename(ref_date = year_month) %>%
  mutate(ref_date = lubridate::make_date(ref_date)) %>%
  select(everything()) -> master_construction

master_provincial_table <- left_join(master_construction,master_provincial_table)
# saving the CSV {} between the
```

these other two tables that I am not sure if I will include

```{r eval=FALSE, include=FALSE}
temp <- get_cansim_ndm("34-10-0163-01")
temp %>% clean_names() -> temp
view(dfSummary(temp))
```

```{r eval=FALSE, include=FALSE}
temp <- get_cansim_ndm("36-10-0098")
temp %>% clean_names() -> temp
view(dfSummary(temp))
```

### Prices

here in this section I will ad prices

#### CPI

```{r CPI}
cpi <- cansim::get_cansim_ndm(cpi_table_number)
cpi <- janitor::clean_names(cpi)
cpi %>%
    select(ref_date,geo,products_and_product_groups,uom,value) %>%
  mutate(ref_date = parse_date(ref_date, "%Y")) %>%
  filter(ref_date > from_this_year) %>% 
  filter(uom == "2002=100") %>%
  select(!uom) %>% 
  filter(geo %in% provinces) -> temp_CPI  
temp_CPI %>%
data.table::fwrite(here::here("output", str_glue("CPI_{cpi_table_number}.csv")))
  interactive_table(temp_CPI)
  
  temp_CPI %>%
  filter(products_and_product_groups %in% c("All-items", "Goods","Services")) %>%
  pivot_wider(names_from = products_and_product_groups, values_from = value)  -> clean_cpi

master_provincial_table <- left_join(master_provincial_table,clean_cpi) 
```

#### PPD

producer prices

```{r}

```

### Labour force

#### Labour force characteristics by industry,annual 

**LFS survey**

```{r Labour force characteristics by industry, annual}

LFS_annual <- cansim::get_cansim_ndm(annual_lfs_table_number)
LFS_annual <- janitor::clean_names(LFS_annual)
LFS_annual %>%
  select(everything()) %>%
  mutate(ref_date = parse_date(ref_date, "%Y")) %>%
  filter(ref_date > from_this_year) %>% 
  filter(age_group == "15 years and over") %>% 
  filter( sex == "Both sexes" ) %>%
  select(ref_date,geo,labour_force_characteristics,north_american_industry_classification_system_naics,value) %>% 
  pivot_wider(names_from = labour_force_characteristics, values_from = value) %>% interactive_table()

```

#### annual employment by industry SEPH

survey for this is SEPH

this needs to be run by mid feb

```{r annual employment by industry, eval=FALSE, include=FALSE}
employment_by_industury <- cansim::get_cansim_ndm(employment_by_industury_table_number_annual)
employment_by_industury <- janitor::clean_names(employment_by_industury)
employment_by_industury %>%
    select(ref_date,geo,type_of_employee,north_american_industry_classification_system_naics,value,status) %>% 
  mutate(ref_date = parse_date(ref_date, "%Y")) %>%
  filter(ref_date > from_this_year) %>% 
  pivot_wider(names_from = type_of_employee, values_from = c(value,status)) %>% View()
  filter(geo %in% provinces) %>%
  as_tsibble(key = c(geo)) %>%
  group_by_key() %>%
  index_by(year_month = ~ year(.)) %>%
  summarise(across(where(is.numeric),list(sum))) %>%
  as_tibble() %>% 
  rename(ref_date = year_month) %>%
  mutate(ref_date = lubridate::make_date(ref_date)) %>%
  select(everything()) -> master_annual_grain_shipment

```

#### Average hourly earnings for employees paid by the hour, by industry, annual

### [Employment Insurance Statistics ](http://www23.statcan.gc.ca/imdb/p2SV.pl?Function=getSurvey&SDDS=2604 "Employment Insurance Statistics - Monthly")

#### **Employment insurance beneficiaries (regular benefits) by province and territory, monthly, seasonally adjusted**

[14-10-0011-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1410001101&pickMembers%5B0%5D=2.2&pickMembers%5B1%5D=3.1&pickMembers%5B2%5D=4.1&cubeTimeFrame.startMonth=01&cubeTimeFrame.startYear=2018&cubeTimeFrame.endMonth=11&cubeTimeFrame.endYear=2020&referencePeriods=20180101%2C20201101)

Job Vacancy and Wage Survey

# **Employment insurance beneficiaries (regular benefits) by province and territory, monthly, seasonally adjusted**

### agriculture/aquaculture

focusing on agric/aquaculture

#### grain shipments 

```{r grain shipments}
grain_shipment <- cansim::get_cansim_ndm(grain_shipment_table_number)
grain_shipment <- janitor::clean_names(grain_shipment)
grain_shipment %>%
    select(ref_date,geo,type_of_grain,value) %>%
  mutate(ref_date = parse_date(ref_date, "%Y-%m")) %>%
  filter(ref_date > from_this_year) %>% 
  pivot_wider(names_from = type_of_grain, values_from = value) %>% 
  filter(geo %in% provinces) %>%
  as_tsibble(key = c(geo)) %>%
  group_by_key() %>%
  index_by(year_month = ~ year(.)) %>%
  summarise(across(where(is.numeric),list(sum))) %>%
  as_tibble() %>% 
  rename(ref_date = year_month) %>%
  mutate(ref_date = lubridate::make_date(ref_date)) %>% 
  select(everything()) -> master_annual_grain_shipment
master_annual_grain_shipment %>% data.table::fwrite(here::here("output", str_glue("grain_production {grain_shipment_table_number}.csv")))
  
master_provincial_table <- left_join(master_provincial_table,master_annual_grain_shipment)
master_provincial_table %>%  data.table::fwrite(here::here("output", str_glue("provincial_view.csv")))
```

## results

```{r all years master_table}
master_provincial_table %>% 
  mutate(across(where(is.character), as.factor)) %>%
  mutate(ref_date = year(ref_date)) %>%   
  mutate(ref_date = as.factor(ref_date)) %>%
  rename_with(~ tolower(gsub("_", " ", .x, fixed = TRUE))) %>%
  filter(geo != "Canada") %>%
  interactive_table() %>% 
  formatCurrency(3:5, digits = 0)%>%
  formatStyle(
    6,
    background = styleColorBar(master_provincial_table$population, 'teal'),
    backgroundSize = '100% 90%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )  %>%
formatStyle(
    7,
    background = styleColorBar(master_provincial_table$import, 'steelblue'),
    backgroundSize = '100% 90%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )  %>%
  formatStyle(
    8,
    background = styleColorBar(master_provincial_table$export, 'red'),
    backgroundSize = '100% 90%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )  %>%
  htmlwidgets::saveWidget("test.html") 


```

\
year 2020 only

```{r}
master_provincial_table %>% 
  mutate(across(where(is.character), as.factor)) %>%
  mutate(ref_date = year(ref_date)) %>%   
  filter(ref_date == 2020) %>%
  mutate(ref_date = as.factor(ref_date)) %>%
  
  rename_with(~ tolower(gsub("_", " ", .x, fixed = TRUE))) %>%
  filter(geo != "Canada") %>%
  interactive_table() %>% 
  formatCurrency(3:5, digits = 0)%>%
  formatStyle(
    6,
    background = styleColorBar(master_provincial_table$population, 'teal'),
    backgroundSize = '100% 90%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )  %>%
formatStyle(
    7,
    background = styleColorBar(master_provincial_table$import, 'steelblue'),
    backgroundSize = '100% 90%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )  %>%
  formatStyle(
    8,
    background = styleColorBar(master_provincial_table$export, 'red'),
    backgroundSize = '100% 90%',
    backgroundRepeat = 'no-repeat',
    backgroundPosition = 'center'
  )  
```

## tips

maybe use \* in regex to match wild cards with the coordinates; for example 1.1.\*\* \*

use this mutate_at(vars(births:residual_deviation), list(\~ .x - lag(.x))) to automatically create a first difference of any table.

rename_with(iris, \~ tolower(gsub(".", "\_", .x, fixed = TRUE)))

```{r eval=FALSE, include=FALSE}
rename_with(iris, ~ tolower(gsub(".", "_", .x, fixed = TRUE)))


maybe use \* in regex to match wild cards with the coordinates; for example 1.1.\*\*\ *

use this mutate_at(vars(births:residual_deviation), list(\~ .x - lag(.x))) to automatically create a first difference of any table.
  mutate(across(where(is.factor), as.character))
  
  # use this to extract all of the commits for the work you have done
  
  git log --since='last year' --date=short --pretty=format:'%h,%an,%ad,%s' > ~/log.csv


```

### things I should have done

created a schema for naming things; I should have followed the statcan names instead of naming things for simplicity. create code templates with text generations based on three scenarios annual tables weekly tables monthly tables

have a to do list
