---
x---
title: "technical_R_tips" 
author: "ArmanAttaran"
date: "2020-12-01"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---

## Tidyeval/functions in tidyverse

example below is from a [blog](https://www.tidyverse.org/blog/2020/02/glue-strings-and-tidy-eval/) it is useful for creating functions for automating things in IAD

```{r}

library(tidyverse)

mean_by <- function(data, by, var) {
  data %>%
    group_by({{ by }}) %>%
    summarise(avg = mean({{ var }}, na.rm = TRUE))
}


iris %>% mean_by(Species, )



```

## use DT for showing tables

## use plotly for showing graphs

every r scripts needs to follow tidyverse style guide.

use `styler` package to do it.

use stringr to create a naics to description and growth rate

<https://github.com/earowang/tsibbletalk>

use this to create NAICS hierarchy views
---
title: "viz_ideas"
author: "ArmanAttaran"
date: "2020-11-25"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---

## Introduction

these are ideas I have for my own visual analytic template I am not sure how they all fit together But I will store them here as my notes; **please ignore this file**

ggplot2 and plotly will be used throughout; here is the [youtube](https://www.youtube.com/watch?v=h29g21z0a68&t=7867s) video explaining this

# big viz ideas for all data

this little neat idea could be used to build a huge analytic template

this could be good for comparing CPC; for example graph CPC and then we can sort on 31-33 naics

```{r terris, eval=FALSE, include=FALSE}
library(trelliscopejs)
data(gapminder, package = "gapminder")

qplot(year, lifeExp, data = gapminder) +
  xlim(1948, 2011) + ylim(10, 95) + theme_bw() +
  facet_trelliscope(~ country + continent,
    nrow = 2, ncol = 6, width = 300, 
    as_plotly = TRUE, 
    plotly_args = list(dynamicTicks = T),
    plotly_cfg = list(displayModeBar = F)
  )

```

this example could be good for people to select naics to quickly compare a few industries through out time

```{r}
library(crosstalk)
library(plotly)

class(highlight_key(mtcars))

# generally speaking, use a "unique" key for filter, 
# especially when you have multiple filters!
tx <- highlight_key(txhousing)
gg <- ggplot(tx) + geom_line(aes(date, median, group = city))
filter <- bscols(
  filter_select("id", "Select a city", tx, ~city),
  ggplotly(gg, dynamicTicks = TRUE),
  widths = c(12, 12)
)

tx2 <- highlight_key(txhousing, ~city, "Select a city")
gg <- ggplot(tx2) + geom_line(aes(date, median, group = city))
select <- highlight(
  ggplotly(gg, tooltip = "city"), 
  selectize = TRUE, persistent = TRUE
)

bscols(filter, select)
```

second example has even more filtering options

sales could be CPC, cities = naics ; year option could be removed to show case the last 5 years

```{r}
library(crosstalk)
tx <- highlight_key(txhousing)
widgets <- bscols(
  widths = c(12, 12, 12),
  filter_select("city", "Cities", tx, ~city),
  filter_slider("sales", "Sales", tx, ~sales),
  filter_checkbox("year", "Years", tx, ~year, inline = TRUE)
)
bscols(
  widths = c(4, 8), widgets, 
  plot_ly(tx, x = ~date, y = ~median, showlegend = FALSE) %>% 
    add_lines(color = ~city, colors = "black")
)
```

## Bar chart!!! for comparing growth

nice graphing idea for [bar charts](https://themockup.blog/posts/2020-09-04-10-table-rules-in-r/)

# Table ideas

## GT with Html, good for static reports, does not work with interactive stuff

[here](https://themockup.blog/posts/2020-10-31-embedding-custom-features-in-gt-tables/)is a blog describing the GT package with HTML

[guidelines](https://themockup.blog/posts/2020-09-04-10-table-rules-in-r/) for tables
