---
title: "volatility_index"
author: "Arman Attaran"
date: "2020-12-07"
output: workflowr::wflow_html
editor_options:
  toc: TRUE
  toc_depth: 4
  chunk_output_type: console
---

# Executive summary

This is a simple document outlining a proposed method to track volatility of each provincial economy, see [Results] for the actual graphs.

## problem

I needed a metric to show how stable Manitoba's economy really is for the presentation to SUT.

## proposed solution

-   version \#1

    -   simply create a metric that squares the values of CPC and average it by province , by doing so if a there are large contributions either negative or positive by a 2 digit naics it would be exasperated

-   version \#2

    -   take the absolute value of CPC add one to it and then square it and average it by province.

        -   I add one because in version \#1 if a CPC is below 1 (which it usually is) it would decrease the metric after squaring it; I think this is against the spirit of the metric.

        -   I take the absolute value because taking a negative CPC and adding one to it would result in a value below one which makes no sense.

## data cleaning/ prep

here is the code for now I will document it later. it is pretty clean though you will probably understand it just by reading it

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
two_digit_naics_code <- c("[11]", "[21]", "[22]", "[23]", "[31-33]", "[41]", "[44-45]", "[48-49]", "[51]", "[52]", "[53]", "[54]", "[55]", "[56]", "[61]", "[62]", "[71]", "[72]", "[81]", "[91]")
```

```{r echo=TRUE}
PGDPtablenumber =  "36-10-0402"
PGDP <- cansim::get_cansim_ndm(PGDPtablenumber)
PGDP <- janitor::clean_names(PGDP)
PGDP %>%
  select(ref_date,geo,north_american_industry_classification_system_naics,value,hierarchy_for_north_american_industry_classification_system_naics,coordinate,classification_code_for_north_american_industry_classification_system_naics,value_2) %>%  
  mutate(ref_date = lubridate::make_date(ref_date)) %>%
  rename(CPC = value_2) %>%
  filter(ref_date > "2005-01-01") %>%
  filter(value == "Contributions to percent change") %>%
  select(!value) %>%
  filter(classification_code_for_north_american_industry_classification_system_naics %in% c(two_digit_naics_code) ) %>%
  group_by(ref_date,north_american_industry_classification_system_naics,geo) -> clean_PGDP
  

clean_PGDP %>%
mutate(absoluteCPCsquared = (abs(CPC)+1)**2) %>%
  group_by(geo,ref_date) %>%
  summarise(yearly_average_absolute_CPC_squared = mean(absoluteCPCsquared), sd = n()) -> yearly_average_absolute_CPC_squared
```

## creating the metric

```{r echo=TRUE}
clean_PGDP %>%
mutate(CPCsquared = (CPC)**2)%>%
  group_by(geo,ref_date) %>%
  summarise(yearly_average_CPC_squared = mean(CPCsquared), sd = n()) -> yearly_average_CPC_squared
```

## Results

### All provinces

#### the free scale version

##### absolute value and squared version

```{r echo=FALSE, fig.height=12, fig.width=12}
ggplot(yearly_average_absolute_CPC_squared) +
 aes(x = ref_date, y = yearly_average_absolute_CPC_squared) +
 geom_line(size = 1L, colour = "#0c4c8a") +
 theme_minimal() +
 facet_wrap(vars(geo), scales = "free")

```

##### only squared version 

```{r echo=FALSE, fig.height=12, fig.width=12}
ggplot(yearly_average_CPC_squared) +
 aes(x = ref_date, y = yearly_average_CPC_squared) +
 geom_line(size = 1L, colour = "#0c4c8a") +
 theme_minimal() +
 facet_wrap(vars(geo), scales = "free")

```

#### fixed scale version

##### Absolute value and squared version

```{r echo=FALSE, fig.height=12, fig.width=12}
ggplot(yearly_average_absolute_CPC_squared) +
 aes(x = ref_date, y = yearly_average_absolute_CPC_squared) +
 geom_line(size = 1L, colour = "#0c4c8a") +
 theme_minimal() +
 facet_wrap(vars(geo))

```

##### squared version 

```{r fig.height=12, fig.width=12}

ggplot(yearly_average_CPC_squared) +
 aes(x = ref_date, y = yearly_average_CPC_squared) +
 geom_line(size = 1L, colour = "#0c4c8a") +
 theme_minimal() +
 facet_wrap(vars(geo))

```

### Western Canada 

```{r}
yearly_average_absolute_CPC_squared %>%
 filter(geo %in% c("Alberta", "Manitoba", 
"Saskatchewan")) %>%
 ggplot() +
 aes(x = ref_date, y = yearly_average_absolute_CPC_squared) +
 geom_line(size = 1L, colour = "#0c4c8a") +
 theme_minimal() +
 facet_wrap(vars(geo))
```

```{r}
yearly_average_CPC_squared %>%
 filter(geo %in% c("Alberta", "Manitoba", 
"Saskatchewan")) %>%
 ggplot() +
 aes(x = ref_date, y = yearly_average_CPC_squared) +
 geom_line(size = 1L, colour = "#0c4c8a") +
 theme_minimal() +
 facet_wrap(vars(geo))
```
